\thesistitle

### 2019-07-30 sections/clonerefactor.tex
Removed these categories that I don't quite like
Other

\subsection{Contents}\label{sec:setupcontents}
Finally, we looked at what nodes individual clone instances span. We selected a set of catagories on basis of empirical evaluation of a set of clones in our dataset. We selected the following categories to be relevant for refactoring:
\begin{enumerate}
  \item \textbf{Full Method/Constructor/Class/Interface/Enumeration:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
  \item \textbf{Partial Method/Constructor:} A clone that spans (a part of) the body of a method. The declaration itself is not included.
  \item \textbf{Several Methods:} A clone that spans over two or more methods, either fully or partially, but does not span anything but methods (so not fields or anything in between).
  \item \textbf{Only Fields:} A clone that spans only global variables.
  \item \textbf{Includes Fields/Constructor:} A clone that spans a combination of fields and other things, like methods.
  \item \textbf{Method/Class/Interface/Enumeration Declaration:} A clone that contains the declaration (usually the first line) of a class, method, interface or enumeration.
  \item \textbf{Other:} Anything that does not match with above-stated categories.
\end{enumerate}

@@

\subsubsection{Partial Method/Constructor}
These categories describe clone instances which are found in the body of a method or constructor. These clones can often be refactored by extracting a new method out of the cloned code. We detect such clones by checking that each node in the clone instance has a parent node that is a methoddeclaration, but none of the nodes is a method declaration. We describe the procedure by with we recursively seek the parent nodes of a node in section \ref{sec:methodlevelcr}.

@@

>>>>

\subsection{Contents}\label{sec:setupcontents}
Finally, we looked at what nodes individual clone instances span. We selected a set of catagories on basis of empirical evaluation of a set of clones in our dataset. We selected the following categories to be relevant for refactoring:
\begin{enumerate}
  \item \textbf{Full Method/Constructor/Class/Interface/Enumeration:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
  \item \textbf{Partial Method/Constructor:} A clone that spans (a part of) the body of a method. The declaration itself is not included.
  \item \textbf{Several Methods:} A clone that spans over two or more methods, either fully or partially, but does not span anything but methods (so not fields or anything in between).
  \item \textbf{Only Fields:} A clone that spans only global variables.
  \item \textbf{Other:} Anything that does not match with above-stated categories.
\end{enumerate}

@@

\subsubsection{Partial Method/Constructor}
These categories describe clone instances which are found in the body of a method or constructor. These clones can often be refactored by extracting a new method out of the cloned code. We detect such clones by checking that each node in the clone instance has a ancestor node that is a MethodDeclaration, but none of the nodes is a method declaration. We describe the procedure by with we recursively seek the parent nodes of a node in section \ref{sec:methodlevelcr}.

@@

\subsubsection{Other}
The ``Other'' category denotes all configurations of clone contents that do not fall into above categories. Often, these are combinations of above states concepts. For instance, a combination of constructors and methods is clones, or a combination of fields and methods. Such clones indicate, like the ``Several Methods'', the requirement of performing a more architectural-level refactoring. These are often more complicated, especially when aiming to automate this process.
